
# Simple Linear Regression

```{r}
library(caTools)
library(ggplot2)
```


```{r}
# Importing the dataset
dataset = read.csv('Salary_Data.csv')
head(dataset)
```

```{r}
# Splitting the dataset into the Training set and Test set
set.seed(123)
split = sample.split(dataset$Salary, SplitRatio = 2/3)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)
```


```{r}
# Fitting Simple Linear Regression to the Training set
regressor = lm(formula = Salary ~ YearsExperience, data = training_set)
# to get details of regressor
summary(regressor)
```

```
Coefficients:
                Estimate Std. Error t value Pr(>|t|)    
(Intercept)        25592       2646   9.672 1.49e-08 ***
YearsExperience     9365        421  22.245 1.52e-14 ***
```
Here 3 star means it is highly statistically significant.  And no star means that 
it is not statistically significant.

__Statistical significance__ is the likelihood that a relationship between two 
or more variables is caused by something other than chance. Statistical 
hypothesis testing is used to determine whether the result of a data set is 
statistically significant. This test provides a p-value, representing the 
probability that random chance could explain the result. In general, a p-value
of 5% or lower is considered to be statistically significant.

#### Predicting the Test set results

```{r}
y_pred = predict(regressor, newdata = test_set)
y_pred
```

#### Visualising the Training set results

```{r}
ggplot() +
  geom_point(aes(x = training_set$YearsExperience, y = training_set$Salary, color = 'blue')) + 
  geom_line(aes(x = training_set$YearsExperience, y = predict(regressor, newdata = training_set), color = 'red')) +
  ggtitle('Salary vs Experience (Training set)') +
  xlab('Years of experience') +
  ylab('Salary')
```


#### Visualising the test set results

```{r}
ggplot() +
  geom_point(aes(x = test_set$YearsExperience, y = test_set$Salary, color = 'blue')) + 
  geom_line(aes(x = training_set$YearsExperience, y = predict(regressor, newdata = training_set), color = 'red')) +
  ggtitle('Salary vs Experience (Test set)') +
  xlab('Years of experience') +
  ylab('Salary')
```










